%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%
% 										 THE SHORT, THE DARK, THE TWISTED STORY COLLECTION 									%
% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %
% Short stories written by Miguel Gómez Casado (a.k.a. Crazy Jäger) 																		%
% --------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- 	%
% Document started on October 2020																							%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%
% 											PAQUETES Y CONFIGURACION DE DOCUMENTO										%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%

% Tipo de documento
\documentclass[a4paper,onecolumn,11pt]{article}

% Idioma y juego de caracteres
\usepackage[british,UKenglish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% otros paquetes (esteticos)
\usepackage{graphicx} % Necesario para la inclusion de imagenes
\usepackage{booktabs} % Necesario para la mejora en la decoracion de tablas
\usepackage[toc,lot,lof]{multitoc} % Indices a dos columnas
\usepackage{float} % Para fijar las imagenes y tablas
\usepackage{anysize} % Permite cambiar tamanno de margenes
\marginsize{2cm}{2cm}{2cm}{2cm} % Tamanno de los margenes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%
% 												INFORMACION DEL DOCUMENTO											%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%

% Composicion de Portada
\title{
\textsc{\normalsize Short Story Collection} \\
\vspace{1cm}
\hrule
\vspace{0.4cm}
The Short, The Dark, The Twisted
\vspace{0.5cm}
\hrule
}
\author{Gómez Casado, \textsc{Miguel} (a.k.a. Crazy Jäger) }

\date{\today} 

\begin{document}

\maketitle % Insertar portada

\begin{abstract}
This document includes a collection of short stories I have written, most of them as a result of challenges or petitions. You may find more information about the situation this stories were written in and maybe some of the inspiration (usually keywords or a particular topic) that drove me to write this stories in the appendix. Feel free to download them and read them and share them if you like them. It would be much appreciated. This document has been written using LaTeX. 
\end{abstract}

\newpage

% Composición del Indice
\hrule

\tableofcontents % Componer y mostar el indice

\hrule

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%
% 												CONTENIDO DEL DOCUMENTO												%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%


\section{The Prince's Fever}

A long time ago, in a kingdom long lost in the books of history, there lived a fair and rightful princess. Everyone respected and loved their ruler. The day she married a young prince, the entire kingdom celebrated for days without end. The merry couple looked merry indeed. They became like heart and soul, never leaving each other's side, not for a second. This all changed one day. Oh how the kingdom grieved when they learned that the young prince had fallen terribly ill.\\
\newline
The princess called in all the doctors in the kingdom, but not a single one of them could identify the prince’s affliction. The princess then sent out word that whomever brought her the cure for this illness would be greatly rewarded. Adventurers from all over the world came to the kingdom to try their luck, but none succeed. The prince’s condition worsened by the day.\\
\newline
Ser Brydon, the valiant, a renowned knight of the kingdom was one of the first to leave in search of the cure. He was one of the last to come back from his months long quest. Entering the throne room, he knelt before his princess and told her that he had found what she was looking for. The princess, with a new found hope, listened to the knight. An old wizard, whose name was long forgotten, knew a spell that could bring the prince back. However, he would need her to be present in the ritual.\\
\newline
The princess put on her travelling garb and made haste alongside the knight. For many days and many nights they rode, finally reaching a small shack in the woods from the other side of the kingdom. The wizard performed the ritual and they both thanked him before returning to the castle. Upon arrival, they found the gate locked shut. The princess called to the watchmen. The prince appeared before them from the gate tower raising his hand in salute. The princes got off her horse and begun to run towards the gate.\\
\newline
The knight realized the prince was wearing his war robes. He called out, but it was too late. The prince lowered his hand and the sky turned black as the thousands of shafts rained upon the princess and her knight. Satisfied with the success of his scheme, the prince turned to face his great new army. Glorious plans awaited him...

\newpage

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{Who's in my house?!}

It must have been two or three o’clock in the morning when he heard the noise. He opened his eyes in a panic. What was that noise. He sat up in silence on his bed, trying to make out what the sound was. The light from the street lamps dimly lit the room. His face had the wrinkles that come with age, his gray hair neatly combed, despite the odd hair sticking out due to the pillow's natural tendency to destroy ones hairdo.\\
\newline
Three clocks chimed in unison on his bedside table, one on top of the Bible he kept close by at all times. Christ watched over him from the cross he hung on top of his bed, as he continued to listen. A few minutes had passed by, and he now identified the origin of the sound. He stood up, his face full of rage and anger. Putting on his slippers, He dragged his feet across the long corridor that separated his bedroom from his study. He knew it. His daughter, she must have made a copy of his key and gone over to his home at night, that stupid witch! He was well aware about his daughters’ conspiracy against him. Both his daughters were working behind his back, trying hard to prove that he was mentally incapable. One of them had surely snuck up to his apartment at night to steal his documents, no doubt.\\
\newline
He reached the room and opened the door. Everything was quiet. The lights were off. He stood there, puzzled. Had he imagined it. He then heard a chuckle coming from the living room, some meters down the corridor to his left.
``Who's there?!'' He demanded, ``who's in my house?!''.\\
``It's me, dad'' the voice of his oldest daughter replied, ``we have come to take your money, so you don't pay any more to that sect of yours''.\\
\newline
He went red in fury. How dare her, of all people, a bloody atheist, dare to call his community of fellow followers of Jesus Christ a sect! He rushed towards the living room as fast as his aged legs allowed him to. When he got there, the lights were off, but he could feel her presence. He switched the lights on only to find\ldots nothing. The room was empty. \\
\newline
Another chuckle came from behind. He spun around.\\
``The devil has taken you both!'' He shouted into the darkness.\\
``And he will also take your grandson,'' replied the voice of his youngest daughter, ``we will make him one of us!''
``Don't you dare, bitch!'' He shouted at her, as he began marching down the corridor towards the kitchen, where the voice came from. He was midway when his other daughter called from behind.\\
``Your money will be ours, old man! Our plan to poison you at the day care centre might have failed, but we will kill you eventually!''\\
\newline
He turned and found himself face to face with the lady he had hired to look after him, a worried expression on her face.\\
“Are you ok, sir?'' She said.\\
And then he realized. The other day she had cooked him a meal, and he had been ill all day, throwing up and going to the bathroom. She was one of them. She also wanted to kill him, all of them did. His daughters, his doctor, the nurses at the day care centre he had quit, and now even her. He rushed towards his room, seeking the protection of The Lord.\\
\newline
He tripped over the carpet and fell hard on his head. He tried to move, but his legs wouldn’t respond. Neither did his arms. He heard the maniacal laughter of his daughters, and also the laughter of whom only could be Satan himself. He closed his eyes and began to pray. He then heard the voice of his younger daughter, but it was different, it was full of sadness. He could feel her fighting of her tears.\\
``Dad\ldots you are ill\ldots'' she said.\\
``NO!'' He answered back, ``I know what you are doing! I am not ill!''\\
``You are, dad... you are very ill\ldots''\\
``And what is the name of my affliction, then?!'' He barked back.\\
After a pause there was nothing but silence. And then, he heard a whisper. It was his own voice:\\
``Alzheimer’s disease...''

\newpage

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{One single survivor}

I sat on my seat for a while before shutting down the engine to gather my thoughts. I opened the door and came out of my car. The police that had arrived before me had already established a perimeter around the house. My partner was running late, as usual, so I figured it might be a better idea to start without him. I walked up to the door. As I did so, I passed by an ambulance. A young girl was nodding at an officers questions, but I could tell her mind was somewhere else. She rocked back and fro very slowly, and her eyes were fixed in the horizon. The signs of shock were clear as daylight in her, she wasn’t supposed to have survived the horrors from within the building.\\
\newline
I showed my badge to the officer guarding the door, and he let me through. The forensics team had already arrived. They were all over the place, taking samples of everything, taking photographs of everything\ldots I walked into the living room and was instantly punched in the face by the stench of blood and alcohol. When I mastered the strength to look I was even more horrified. The entire room was splattered with blood. Floor, walls, even the ceiling. Bodies littered the floor. I counted fifteen in total. I took note of what I saw and walked up to one of the forensic scientists on site.\\
\newline
``What happened here?'' I asked.\\
He looked up at me and removed his mask to speak clearer.\\
``Fifteen victims, all between the ages of 15 and 17''.\\
``Underage\ldots'' I muttered, as I wrote down the details, ``I smell alcohol''.\\
``Correct. It all seems to point towards an illegal party of sorts. Binge drinking, drugs, sex\ldots''\\
``What's the preliminary cause of death?'' I enquired, dotting down the last remarks I had been given.\\
``It's too soon to determine. None show any sign of blunt trauma and we haven't found any traces of gunfire or blades of any kind. They all seem to have died from internal bleeding, although we will not be able to determine what caused it until after the autopsy''.\\
\newline
I thanked him and moved out of the room to allow them to continue with their work comfortably. I bumped into the inspector that had been questioning the girl outside.\\
``She was the only survivor,'' he said, ``according to her statements, everyone started vomiting blood at some point. She got out when it started''.\\
``Poison?'' I asked.\\
``Maybe. She had drunk alcohol, in spite of being 16. I think the experience sobered her up though. Do you think they poisoned the food or drink?''\\
``Could be a possibility, I suppose. We will have to wait for the mad scientists inside to come and determine that''.\\
He chuckled at my remark, and then went out. I checked around the house a little bit, just in case. The forensic team would have to search more thoroughly, but every little helped, just to make sure nothing was left behind from that nightmare.\\
\newline
I stepped into the cool night air, breathing some clean oxygen at last. The ambulance had gone, and I saw my partner standing nervously next to my car. I sighed and walked over to him.\\
\newline
``A girl made it out alive, the other 15 in the party died'' I briefed him, ``she will be taken to the local hospital. She will need police protection for the time being''.\\
``You want me to take charge?'' he asked.\\
``Yes'' I answered.\\
\newline
Reaching into one of my coat's pockets, I produced one of the vials. ``Make sure this gets into her system, I don't care how, just make sure it does\ldots''.

\newpage

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{Into the dark}

He opened his eyes, but it made little difference. The room he was in was pitch black. Not a single particle of light was around to show him where he was. He felt the floor with his hands. The cool smooth surface of stone was the only stimulus he found. The stone was polished, smooth to the touch. This floor was manmade. He stood up with some difficulty, not knowing which direction was which and having only the stone floor as help.\\
\newline
A sharp throbbing pain in the back of his head made him a little dizzy. He felt a bump when he touched the spot where the pain originated. That was an explanation as to why he didn’t know where he was and how he had gotten there. He began walking forward, placing his hands in front of him in order not to crash into something and dragged his feet slowly as to not trip.\\
\newline
``Hello?'' His voiced echoed in the darkness, ``is there anyone there?''\\
\newline
The silence was the only response he got. He continued to walk forward, or had he started walking in circles? He couldn't tell.\\
\newline
``If there is anyone out there, please answer me!'' He pleaded, slowly giving way to the panic that had started to build up.\\
\newline
``I don't know what you want from me, but please, I will give you whatever you want, just let me go!''\\
\newline
He stopped dead in his tracks when he heard a gentle rattling sound that echoed away. It was a sound that would usually be associated to chains being dragged along the floor.\\
\newline
``Who's there?'' He said, raising his voice, failing to mask the fear he was feeling right now.\\
\newline
The sound of chains got louder.\\
\newline
He took a step backwards. Something blocked his ankle as it tried to move back, causing him to trip and fall over. He fell on his back, pain shooting up his coccyx as he hit the cold floor. The chains were getting closer. He started dragging himself backwards. He then retreated his hand as he touched something warm on the floor. It was some sort of liquid. It felt thick and sticky.\\
\newline
The sound of chains was getting louder, and he began to hear heavy breathing. He started to crawl backwards, but he met a wall. The sound of chains stopped. All he could hear was his own breathing and that heavy breathing he had heard before. It sounded as if the one breathing was right in front of him. It was the sort of breathing someone had when they were chocking.\\
\newline
``Who...?!''\\
\newline
A hand suddenly covered his mouth. It was warm and sticky, like the substance he had touched earlier. Some of it went into his mouth. He felt his entire mouth go numb. The breathing in front of him git heavier. It started to produce a sort of growling sound in between breaths. He felt his heart pounding and then he felt warm breath gently caress his ear.\\
\newline
``Hush little lamb,'' said a calm gentle voice, ``you will only make it kill you faster\ldots''.\\
\newline
He tried to scream but the numb mouth and the hand covering it stopped him from doing so. The voice laughed gently beside him. He felt great pain in his chest and then everything drifted away. The pain, the fear, the laughter and life\ldots it all drifted away into the dark.

\newpage

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{The special cookies}

There was once a small town in the middle of country side County Roscommon Ireland. Slightly far off from every other little bit of civilization. When the British invaded Ireland, this town was kept hidden. It became self sufficient, it had every resource it needed. A short trip to the Shannon provided fresh water and fish. There was enough space to grow a few crops and herd animals, and the surrounding forest provided plenty of fruit during the summer and wood during the winter. It even had its own small church, were religious ceremonies could be held undisturbed, even during the ruthless reign of Elisabeth I. For centuries, this town remained hidden, thanks to the forest around it.\\
\newline
One day, the local lumberjack, who went a little too deep into the forest to get some wood for the night's fire heard a gentle singing. Curious, as he was, he sought out the origin of the singing. After a few minutes, he came across a small wooden makeshift stall. A little girl, probably about six or seven years old was sitting by herself, humming the song he had been hearing. She was dressed in what looked like an assortment of rags, carelessly sown together in a seemingly random pattern. She, however, had well combed golden hair that fell behind her in two neat braids, and a chubby face riddled with freckles. A wide smile was draw on her face as she continued to hum the melody. On the stall was a small variety of sweets. These included small cakes and pastries, as well as scones. In the middle, however, there was a small mound of cookies that looked particularly appetizing.\\
\newline
The lumberjack walked towards her. When she noticed the man, she stopped humming and widened her smile.\\
\newline
``Hello, sir. Would you like to buy any homemade sweets and pastries?'' she asked in a kind tone.\\
\newline
The lumberjack, puzzled at first, decided to ask for a few cookies. She smiled as she wrapped them gently in a piece of paper she produced from a small drawer on the stall. The lumberjack took a bite of the cookies. They had a sweet taste and a slightly refreshing herbal aftertaste to them that made them absolutely delicious. He had never tasted such delightful sweets before. By the time he had got home, he had no cookies left. He had eaten all of them. They were so good, he couldn't resist the temptation of eating them.\\
\newline
He thought for a moment that it was odd for such a little girl to be alone in the woods like that, but they were used to it being quiet and calm around, so he thought her parents had probably considered that it was safe for her to be there, plus there would get a little extra income for the sweets. He told the townsfolk about the little girl in the woods, and they all listened to him in amazement, not really believing him.\\
\newline
The next day, several people followed along with the lumberjack, who took them down the route he had followed the day before. When they were a good distance away from the town, they started hearing the song the little girl hummed. They eventually reached her stall. She was very happy to see more people, and greeted them with a very wide smile. They all bought a few pastries and sweets, and of course the cookies. The cookies were exceptionally good, they all agreed. Just like with the lumberjack the day before, no cookies got home, they were too good.\\
\newline
As the next few days passed by, everyone had started going to visit the little girl in the woods. They all enjoyed talking to her and buying her treats. She always seemed to have cookies, even though everyone ordered more and more each time. The cookies never reached home, no matter the amount, they were always eaten on the way home. They were too damn good. The townsfolk started to get fatter and fatter with all the cookies, but they didn't care. The girl was so sweet and her cookies were so good, they couldn't help it.\\
\newline
One day, the group of townspeople that used to go first to see the girl came back shocked and confused. The girl was gone. She was nowhere to be found. Days went by and the girl never appeared again in her usual spot. However, all the townspeople craved the cookies more and more. They started becoming grumpy and aggressive to each other. All the other food tasted like ash. Nothing was good anymore, only the thought of the delicious taste of the cookies. They started to grow hungry. They stopped cooking food, because it tasted so foul to them now. Life was grey without the girl's cookies. They, however, were still fat, and always hungry. They were hungry for the girl's cookies.\\
\newline
One day, the local priest came out of the forest with a face of satisfaction. A few cookie crumbs on his tunic gave it away. They all accused him of kidnapping the girl, keeping her prisoner or as a slave, and demanded that he told them where she was. He refused at first, saying that he had done nothing to her, that he had just casually found her in the woods. The townspeople, who all craved the cookies so badly, started to torture him. They started broke his knees and elbows with hammers and started cutting his stomach, then pouring salt and vinegar on the wounds. The torture continued for several days until he broke and told them were he had seen the girl. A small group of townspeople went to look for her. The injuries sustained by the priest were so grave he died shortly after their departure.\\
\newline
Several days went past and none of the people that had left came back. People in the town started to become paranoid. They had kept the girl to themselves! They wanted all the cookies to themselves. They grew hungrier and hungrier and none of the people who had left were coming back. Everyone locked themselves in. They didn't go outside anymore. The crops died, the animals they kept started to starve or die of thirst and there was an overwhelming feeling of death and negativity looming over the town.\\
\newline
After several weeks, the group of townspeople finally returned. They were all fatter than ever, and their wide grins and full bellies gave them away. The lumberjack, who had stayed in the town, went out of his home and walked up to one of the people who had just returned.\\
\newline
``We have great news!'' announced one of the returning townspeople.\\
\newline
Without warning, the lumberjack pushed the man, who due to his oversized tummy tumbled over with ease. He then threw himself on top of him and started brutally chomping at his oversized belly until it burst open like an overripe tomato. The others watched in horror as the crazed lumberjack feasted upon his former neighbor. The others that had been locked up started to emerge from their homes. They all had crazed eyes and were salivating considerably. They brought every type of weapons with them: axes, knives, hammers, hoes, pitchforks\ldots \\
\newline
The returning people started to turn back in fear, but the others caught up easily and started slaughtering them like animals. At some point, the aggressors started attacking each other too. What had once been a quiet town had now become a crazed frenzy of blood and gore. Former friends and neighbors were killing each other and tearing their intestines and viscera out. At sunset, only the lumberjack remained. He had lost an arm and was fighting to keep his guts from spilling from a gushing wound in his chest.\\
\newline
He started to hear a familiar hum, and looked up. The little girl emerged from the forest, singing her cute little song, so out of place in this bleak scenario. The lumberjack watched her as if she was some sort of deity or angel, not daring to even speak to her. She walked up to the fattest of the dead corpses. The one next to the lumberjack. The one who was the first victim of the killings. The girl then produced a sharp knife from a basket she carried and started to slowly carve the fat out of the dead man's oversized belly and putting it in the basket, humming her song all the way. She noticed the lumberjack and smiled her wide smile at him.\\
\newline
``Would you like some cookies, sir? I will have a fresh batch baked for tomorrow just for you! I just need to collect the ingredients first...''\\
\newline
The lumberjack grinned and nodded, saliva mixed with blood started to drip down the side of his mouth.

\newpage

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{Taming a T-Rex}

Do you even know how many theories about how the world is supposed to end there are out there?! Global pandemic that wipes out humanity. A nuclear war that would literally reduce the world to ashes. Global warming making us all fry in the street. A zombie apocalypse. God’s angels falling upon us with weird ass trumpets, just before every single imaginable natural disaster takes place at the same time to drag us all to hell. And the list can go on for ages!\\
\newline
What did we get?! Some scientist playing god with time and space throwing us all back to the Cretaceous Period. Classic. At least I wasn’t alone, I guess… Even though everyone got thrown randomly at different moments in time and space, I ended up landing with Kiti and Reflex in the same place. Looking at it on the bright side, as I tend to do, they both had somewhat more knowledge as to what to expect here. They both play Ark, that survival game with dinosaurs in it. Played? Will play? I dunno! I suppose time doesn’t make sense anymore after this shenanigans took place\ldots \\
\newline
At first it looked like one of those memes where they talk about a specific topic and someone walks in with a t-shirt that says: ``the expert’’. But they DID have a better idea of what they were doing. My experience with survival was limited to shitty TV shows of people in the middle of nowhere that ``just so happen’’ to find a dead goat and decide to only eat the eyes. That and whatever Minecraft taught me regarding survival, which isn’t much\ldots \\
\newline
I just let them take the lead. They made the decisions while I just went ``stick!’’ and brought a stick back as it was now a valuable resource useful for making all sorts of tools. 
I’d actually say Kiti was really the one in charge, I guess. At least she was the one that probably came up with some of the best ideas we had around concerning finding resources and having a somewhat more comfortable lifestyle. I think Reflex was a bit more concerned about setting up defences against the huge behemoths we had to share this world with now, at least to keep them away from where we had decided to set up camp. I feel like an ant that could easily be stepped on by one of these things and it wouldn’t even notice\ldots \\
\newline
So, thing is, at some point Kiti decided to try and tame one of the dinos. Just for shits and giggles or to see if it more or less worked. She started with one of the small herbivores, at least to test it out. Worked out pretty well, to be honest. We ended up having something like a farm going on. Dodo’s ARE just big dumb birds. I do think both Reflex and I started to get a bit concerned when she started to bring back ``bigger friends’’ home\ldots \\
\newline
She started to bring in carnivores that, I guess, were useful for hunting. Unlike what one would expect with, let’s say a husky, for example, if these guys threw a fit, they would scratch and bite a lot. After about two weeks we all had more scratch marks than ``ok’’ skin. Zero joked around with it saying they were ``battle scars’’. It was definitely better than saying, ``our pets did it’’. It kind of feels like the equivalent to ``dog ate my homework’’ excuse. I do mis doggos tho\ldots \\
\newline
Anyway, as I was saying before, Kiti was starting to bring bigger and badder dinos home. I think we all knew where this was going, just didn’t want to address it at the moment for whatever reason. Maybe we should have. \\
\newline
It happened while having dinner, when she suddenly prompted that she had thought of a plan to capture a T-Rex. I was not amused. At all. I think Zero liked the idea. Having a T-Rex would make us more or less untouchable to most of the threats out here, I’ll give it that, but what worried me was how on earth we would manage to do such a thing. She just shrugged it off as: ``I have a good plan; I’ve given it a lot of thought and I’m sure it will work’’.\\
\newline
Everything she had come up with had worked well so far, so even if I was a bit sceptical at first, I decided to agree. After all, I kind of was alive thanks to her ideas and to Zero’s defence efforts.
The next few days we worked hard gathering a bunch or resources. She didn’t want to bore us too much with the details as to not make us lose focus, so we went step by step. From what I gathered based on what we were doing, we were changing a specific area in a nearby jungle, creating a sort of one-way passageway. It was a very primitive hunting strategy that has always worked. Channelling a target into a controlled scenario where the hunters (in this case us) could easily have the advantage over a bigger foe. This was used with mammoths, sabretooths and the like; so, it did seem like a solid plan.\\
\newline
We had almost everything set up. Next part was adding traps. I guessed what Kiti had been doing for the past days when she handed Reflex and I a shit ton of narcotic berries. Our backpacks were full to the brim with them. It did make sense that we needed a lot for a big guy like the one we were planning to capture.\\
\newline
She sent us to separate areas of the ``channel’’ we had set up. Kiti would prepare the initial bate at the mouth of it to get the T-Rexes attention. Zero would make sure it kept coming down the passageway by adding some more bait, but with some narcotic in it to slowly drain the T-Rex’s energy and my part was basically a fail safe in which I planted some small spikes in a pit to inject some extra narcotic juice in case it failed. They were small spikes as to not hurt the Rex too much, but enough to get some extra narcotic in.\\
\newline
We all got to work in our own separate area. I was starting to plant the spikes when I heard something like a scream in the distance. I thought it must have been the wildlife as some of the scaled creatures around us did emit a human-like screech and continued working as if nothing. When I heard thumping behind me, I realized it was something else\ldots \\
\newline
Huge T-Rex just comes out of nowhere, charging down the passageway. I try to run but meet the wall we had put together at the end of the pathway. I turned to face the T-Rex. I was doomed. I noticed something hanging from its teeth\ldots \\
\newline
A backpack?!\\
\newline
``It’s an all-win situation! I have to share less food and get a big pet to keep me protected. Bait worked beautifully I think…’’ said Kiti from a walkway above me, ``just make sure you keep that backpack well strapped to you. I think Zero’s narco-berries weren’t enough’’.

\newpage

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{Mission to Mars}

The time had come. We all sat on our seats quietly. Nervous glances were shared with one another. The countdown for the rocket's launch booming through the speakers, but our nerves turned the words into random noises and gibberish. So, this was it then? Were we about to make history? Was this mission to Mars going to be successful. Only time would tell\ldots \\
\newline
3\ldots 2\ldots 1\ldots \textsc{BLASTOFF}\\
\newline
We had all received training for this, but the real thing still kicked our faces like a mule. One could easily feel the pressure on their face caused by the rapid ascent. I barely managed to move my head around to see how people were doing around. Kitiara and Zeroreflex seemed to be ok so far. Mission was, figuratively speaking, simple. What we had to do was make sure that everything on the station they were building on Mars was doing fine. That and starting arrangements for a bigger mission that was scheduled for some days after our arrival. It wasn't anything too complicated. It was mostly the whole traveling out to space aspect of it what bugged me a wee bit.\\
\newline
I passed out. Don't remember when or for how long, but woke up to Zero throwing stuff at me to get me up. We were already in Space and slowly making our way to Mars. The first critical moment was over, so we allowed ourselves to relax a bit being goofy around the cabin. There really wasn't much to do but we somehow worked it out.\\
\newline
When the landing procedure started, we all sat down again on our seats and waited for it to happen. Bless whomever came up with the idea of autopilots. This handy thing allowed us to sit down and relax while the whole thing happened without us having to do a thing. We panicked a little when the rocket swayed slightly off-course due to a sandstorm that was happening when we arrived. There was a lot of "thunking" going on below us and it was kind of unsettling, but we were ok when the ship finished landing, which was what mattered, right?\\
\newline
We got off the rocket and started moving things from the rocket into the half built station we were going to call home for some time as soon as the sandstorm lifted. We were also allowing ourselves to relieve some stress from the past hours by joking around and saying the stereotypical words often related to famous space travelers from movies. Kitiara noticed a very ugly scrape at the bottom of the ship, we figured it was probably the noise we had heard. A closer inspection showed that some of the insulation material was visible in the center of it. Good thing we saw it. Luckily we were going to have time to look into it and try to fix it. It would only become an issue if we decided to take off again with the rocket in that state as the descent into the Earth's atmosphere could make it ignite.\\
\newline
The inside was funny looking. It felt like we had arrived at some place in the world of "Subnautica", but without all the water. They were the white, circular passageways almost identical to those in the game. We were pondering whether NASA had had a copyright claim or not. We each located our separate rooms and unpacked the few personal items we had brought with us in about 15 minutes. We spent the rest of the day taking inventory of the resources we had brought and the items we might need to repair the rocket. Everything seemed to be in order for us to survive for a long time, comfortably I must add.\\
\newline
The next morning we had breakfast together at the cafeteria. It was a big place as it was supposed to be occupied by many people at some point. That was the target of the overall mission. We were just one of the small missions that would pave the way towards that aim. There was still much work to be done, mind you, otherwise they wouldn't have sent us. It's funny how they managed to package cereal in a way that it looked and tasted the same as back home in spite of the pressure and other hazards it had been subjected to on the way here. Powdered milk was not so good in my opinion, but that's because I just don't like it to begin with. It's just water mixed with ``magic powder'' after all.\\
\newline
After breakfast we all got to work on our tasks. Filled the oxygen tanks from our suits and away we went onto the planet's surface. We had to put up the energy infrastructure for upcoming missions. There was already a small power grid going on, but only the cafeteria and a few more places had electricity in them, mostly the essentials to procure food, water and oxygen. Rooms and corridors relied on sunlight to be lit. Thankfully they had included bathrooms in the priority list of the previous mission. Otherwise it would have been funny.\\
\newline
I started to solder together some of the support beams for the new solar panels we had brought. Zero went over to work on the wiring and Kitiara went to configure the terminals for the energy distribution in the sectors that still had no power in them. We knew this was going to take several days, so we weren't in a hurry or under too much pressure.\\
\newline
Work continued to go normally after lunch break. We joked around at lunch time when we had potatoes and recreated some of the lines from "The Martian" staring Matt Damon. I was still thinking about it when I heard Kitiara's voice over the intercom, asking us both to go to sector C. She had a worried tone in her voice. When we arrived she has nervously typing into one of the terminals. We could hear her breathing heavily from under the suit, so it was clear she was agitated.\\
\newline
``What's wrong?'' asked Zero.\\
``The energy consumption of the oxygen block has halted'' answered Kitiara in a flat tone of voice.\\
\newline
Zero and I looked at each other.\\
\newline
``What does that mean?'' I asked.\\
``It means no oxygen is being produced'', she answered, ``the system states that it halted for security purposes. In order to verify what is happening, we need to go there and assess the situation ourselves''.\\
\newline
We grabbed a bunch of straws from the cafeteria, cut one in half and then pulled out a straw each from Kitiara's hand. I got the short straw, so I went over to investigate. The block seemed to be fine on first glance, but there was an error message on a screen next to the electrical system stating the message previously mentioned by Kitiara:\\
\newline
<<\textsc{WARNING: SYSTEM OFFLINE DUE TO SECURITY PROTOCOLS}>>\\
\newline
I looked for a terminal I could get on to run a diagnostic check to see what was going on. I found one and typed in the command. A few seconds later, a red flashing screen popped back up on the screen of the terminal:\\
\newline
<<\textsc{CRITICAL FAILURE: HULL INTEGRITY COMPROMISED}>>\\
\newline
I froze. The message also showed what seemed to be a map of the oxygen block. The central part of the roof was highlighted with a flashing red color. I exited the block and went over to the maintenance ladder on one side of the sector to climb up. The moment I climbed onto the roof, I realized what had happened. The entire roof was full of scratch marks, the once left behind by a heavy item. The central part was the worst damaged one of all, there was a hole that lead directly into the air purifier. I messaged Kitiara and Zero over the intercom, telling them to come over quick. They arrived in less than two minutes.\\
\newline
``This looks bad...'' remarked Zero as Kitiara carefully walked over to get a better look, ``what do you think did this?''\\
``I'm afraid it was us'', said Kitiara, getting closer to the crack on the roof, ``remember the thumping we heard when we landed? I think we hit the roof\ldots''\\
\newline
``That\ldots that's not possible,'' said Zero after  a while, ``the craft was fitted with an autopilot that would safely land with no damage to the surrounding environment and the occupiers. It isn't possible''.\\
``The sandstorm threw us off course,'' I said, ``maybe that's why we hit the roof?''\\
\newline
Zero hesitated for a bit. After a while his expression changed.\\
\newline
``No!'' he suddenly prompted, making me jump and almost making Kitiara lose her balance as she started to crouch next to the crack, ``the sandstorm changed our landing trajectory, true, but the error should have been calculated by the autopilot, there was no way we could have hit the building! No way at all!''.\\
\newline
We stood in silence for a while. You could feel Zero's confidence in what he was saying. I made a mental note to have a look at the autopilot as soon as I could. As sure as Zero was about his statement, I had had time to inspect the damage on the roof, only visually of course, but I was sure it would match the damage in the lower end of the rocket.\\
\newline
``I don't want to interrupt your little argument about the AI controlling the rocket but\ldots this just got a billion times worse\ldots'' said Kitiara, looking at us.\\
\newline
She was holding a cloth on top of the crack, we could see how it was being pushed upwards. I felt dizzy as I realized what that meant: the oxygen was seeping out.\\
\newline
``We need to seal that crack now!'', shouted Zero, rushing down the maintenance stairs.\\
\newline
We were all starting to panic. Kitiara started to creep away from the crack and was more or less where I was when Zero appeared with the soldering tool.\\
\newline
``You know how to do the soldering, get to work!'' he told me, handing me the tool over. \\
\newline
I crawled towards the crack. I could feel the metal bending slightly under my weight. It was way more damaged than it seemed on first glance. I was next to the crack, I brought my soldering tool closer. I could hear Zero and Kitiara talking, but I had to focus and concentrate. If I sealed this, I would be able to stop the oxygen loss from getting worse, I organized the portable elements of the soldering tool. I put the soldering tool next to the crack.\\
\newline
``Oh, shit! Wait!'' shouted Zero from where he stood. I looked up to see both Zero and Kitiara looking towards me and then it hit me. We had all realized the huge mistake I was about to make, but it was too late, muscle memory got the better of me and I pulled the trigger of the soldering tool. A huge explosion and a ball of flames flung me into the air and off the roof. I feel on the floor and noticed the right side of my ribcage cracking as I hit the floor. Everything faded away slowly.\\
\newline
I woke up wrapped in blankets on the cold cafeteria floor. I tried to move and pain shot up my entire body as I remembered the multiple bone fractures I had sustained in the explosion. Kitiara, who was sitting a few meters away from me walked over with a mug of hot chocolate in her hand and a grim expression.\\
\newline
``We moved the oxygen from the rocket onto the station. We closed off the section, but the explosion and the leak has cost us about 85\% of the oxygen we had''. She handed over the hot chocolate, ``you've been unconscious for two days now. We opened the sweets box. If we are going to die, at least lets die with something nice in our stomachs\ldots''.\\
\newline
Some hours had passed after that last conversation. Nobody spoke again. We just sat in silence, waiting for our doom to come. At night, both Kitiara and Zero were asleep, but I was still feeling bugged about the whole situation, specially the one regarding the autopilot. The silence had allowed me to think, and Zero had been right when he said that it should have been impossible for that to happen.\\
\newline
I stood up as best as I could and shambled over to the closest terminal. I could already feel the lack of oxygen in the air. A feeling of stupor and dizziness. I switched on the terminal, typed the password and proceeded to log into the rockets remote terminal. I wanted to know what had happened, even if it was the last thing I did.\\
\newline
I went over the files and the plan. Everything seemed to have worked as it had been set on the plan. I looked at everything in detail. The execution had been flawless. The recorded deviation caused by the sandstorm had been within the error limits. I checked the log. My eyes widened.\\
\newline
<<\textsc{Plan last modified via remote terminal}>>\\
\newline
I accessed the log. It had been modified from a remote terminal about 10 minutes before landing. How?! Where?! Why?!\\
\newline
I fell to the ground. It was hard to breathe. I could feel my consciousness slowly slipping away. I saw both Kitiara and Zero already passed out where they had decided to sleep, barely breathing. I was still going over it. It was clear now. We had been sabotaged. But in order to remotely change the plan the terminal couldn't have been on earth it had to be the terminal I was just using, but, how?\\
\newline
I looked over to Kitiara and Zero. Their breathing was but a whisper. So was mine. I sheepishly took a look at the corridor on the opposite end. Big yellow eyes with vertical slits for pupils greeted my gaze, a huge toothy grin opening below them.\\ 
\newline
I smiled back, and passed away.

\newpage

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %


% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %
% 													APENDICES														%
% --------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- 	%

\appendix

\hrule

\section{The Prince's Fever}

Written in July of 2019, this story was a result of a Group Event in \textit{Angels vs. Demons}, a group created by my  friend Ruben in a platform called \textit{WeGamers}. To spice things up a little, Ruben always organizes weekly events to make people participate in the group and gives points as a reward that can be used in this platform to exchange for exclusive bundles in certain games.\\
\newline
This event, titled \textbf{\textit{Stories of Princes}} consisted on writing a story that involved a price, either as main character or as a side character.
In this story, I turn what could have been a classic fairy tale story into a much darker and, sadly, realistic story.

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{Who's in my house?!}

This story was written in August of 2019. This was also an event for the \textit{Angels vs. Demons} group in \textit{WeGamers}. The event, titled \textbf{\textit{People and Characters}}, consisted on writing a short story based on someone we knew. This one made me think quite a bit. One day, playing League of Legends, some asshole toxic player made a joke about Alzheimer's disease. My grandfather had died recently as a result of this illness, so it pissed me off a lot. That is one of the reasons why I decided to write this story, in his honour. Alzheimer's disease can kill people. You can try changing my mind, but you will not succeed. My grandfather was already dead the day I visited. The man sitting on the couch with a half broken neck and nothing but hatred and insults for us was not my grandfather.

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{One single survivor}

This story, also from August 2019, was from another event in the \textit{WeGamers} group of \textit{Angels vs. Demons}. The event was titled \textbf{\textit{Terror Story}} and was about writing a horror story. Due to the summer holidays, I watched a lot of \textit{CSI} on television. That probably gave me the idea of writing a police style story, of course, with my particular twist at the end\ldots

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{Into the dark}

In the middle of lockdown in Spain during the CoVid-19 crisis,  Ruben sent out another challenge in his \textit{WeGamers} group \textit{Angels vs. Demons}. The title of this event was self explanatory on the target: \textbf{\textit{Write a poem or short story}}. Poems, I'm not good at. Stories, however, I enjoy writing. This story was partly inspired by the feeling of being trapped and blind to the situation unveiling around us during this period. This would be the last event I would take part in \textit{WeGamers}, as the poor administration of the app (among other things) slowly convinced me to leave the app for good.

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{The special cookies}

One of the options I offer to redeem points on my Twitch channel \textbf{\textit{https://www.twitch.tv/crazyjaegertw}} is for me to write a short story about a particular topic. As you may have guessed, my stories aren't particularly ``child friendly''. A dark twist ending to the story is always the sort of aftertaste I like giving to my stories.
In September of 2020, my twitch friend \textit{QuinzChubb} redeemed this option and asked me to write a story about a \textbf{\textit{Girl selling cookies in the woods}}. If she was expecting a cute story, I am sorry, but that topic was right up my ally\ldots Just not maybe in the way one would expect\ldots

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{Taming a T-Rex}

Once again, the channel points redeem offered on my Twitch channel, now renamed \\\textbf{\textit{https://www.twitch.tv/crazyjaeger0w0}}, has a redeem to make me write a short story. In March of 2021, my twitch friend \textit{KitiaraXVII} redeemed the option and asked me to write about \textbf{\textit{Kiti}}. Even though I had a general idea of what she meant, I asked, and she confirmed she wanted a story about herself. She later specified she would like it to be \textit{Ark} themed (as she likes playing that game a lot) and asked if \textit{zeroreflex93} and myself could be in it. I didn’t really know how to put it together as my stories don’t usually go in this line, but I think I somehow managed to input my little style in here \ldots

% ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- %

\section{Mission to Mars}

Another channel points redemption from my Twitch channel \textbf{\textit{https://www.twitch.tv/crazyjaeger0w0}}. Redeemed at the end of March 2021 by \textit{KitiaraXVII}, she requested a story similar to the previous one in regards to the characters, but themed in space, maybe one of the missions to Mars as it was a hot topic at the time. I wrote this story in Germany during the days I was quarantined on arrival. I spanned it over several days as I was going through a lot of new sensations at the time and was sometimes feeling a bit down. As things started to brighten up, I finished writing this not so bright story\ldots


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%
% 													FIN DEL DOCUMENTO												%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%

\end{document}
